BioTime

### 2020-10-15 data-raw/biotime.Rmd
Move biotime database access to data-raw script.

```{r}
library(here)
library(tidyverse)
library(lazyeval)
library(taxadb)

@@

Import occurence data from Biotime
```{r}
#rdataretriever::install("biotime", connection = "csv", data_dir = here("data"))
# 
# data <- read.csv(system.file("extdata", "biotime/biotime_metadata.csv", package = "biodivTS")) %>%
#   select(study_id, taxa) %>%
#   left_join(read.csv(system.file("extdata", "biotime/biotime_query.csv", package = "biodivTS")), by = "study_id")

data <- pins::pin_get("year-biotime", board = "github")
```

Many of the studies with only one plot have NA for the plot number, but we want to distinguish between NA's in studies that have multiple plots and unlabled studies.
```{r}
#find studies that only have one plot labeled NA
sing_study <- data %>% 
  select(study_id, plot) %>%
  distinct() %>%
  count(study_id) %>%
  filter(n == 1) %>%
  pull(study_id)

#replace plot NA's that are really studies with only one plot with a plot label 
data <- data %>% 
  mutate(plot = case_when(
    study_id %in% sing_study & plot %in% c(NA, "", "#REF!") ~ "A",
    TRUE ~ plot
  ))
```

@@

```{r}
usethis::use_data(biotime_data)
```

>>>>

```{r}
library(here)
library(tidyverse)
library(lazyeval)
library(taxadb)
library(DBI)
library(dbplyr)

@@

Import occurrence data from Biotime

Access database
```{r}
#personal computer
con <- dbConnect(
  drv = RMariaDB::MariaDB(), 
  dbname = "biotime",
  username = "root",
  password = "Ka1172353!", 
  host = "localhost"
)

#thelio
con <- DBI::dbConnect(RMariaDB::MariaDB(), 
                      host="mariadb", 
                      user="root", 
                      password="password", 
                      dbname="biotime")

biotime_sql <- tbl(con, "allrawdata") %>% 
  collect() %>% 
  rename_all(.funs = tolower) %>%
  select(-id_all_raw_data)
```
```{r}
data <- biotime_sql %>% 
  group_by(id_species, plot, year, study_id) %>% 
  summarise(year_abun = sum(na.omit(abundance)), 
            year_biomass = sum(na.omit(biomass))) %>%
  left_join(tbl(con, "datasets") %>% select(taxa = TAXA, study_id = STUDY_ID) %>% collect()) %>%
  left_join(tbl(con, "species") %>% select(id_species = ID_SPECIES, genus_species = GENUS_SPECIES) %>% collect()) %>%
  ungroup()

#should be zero to be appropriately aggregated
#data %>% group_by(study_id, plot, year, id_species) %>% filter(n()>1) %>% View()
```

Replace NA plots with a plot label (these are studies with no plot subdivision)
```{r}
#replace plot NA's that are really studies with only one plot with a plot label 
data <- data %>% 
  mutate(plot = case_when(
    is.na(plot) ~ "A",
    TRUE ~ plot
  ))
```

@@

```{r}
pins::pin(biotime_data, board = "github")
```
